\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{casual}

\usepackage[utf8]{inputenc}

% personal data
\firstname{Lukas}
\familyname{Klingsbo}
\title{Software Engineer}
\homepage{http://lukas.fyi}
%\newline \small{\texttt{\textbf{Homepage: {\color{web}\weblink{http://lukas.fyi}}}}}}
%\title{BCS student of Uppsala \newline \small{\texttt{\textbf{Homepage: {\color{web}\weblink{http://www.mindlevel.net}}}}}}
%\address{Office 719 SEO\\ 851 S. Morgan St.}{Chicago, IL}
\extrainfo{\newline \color{red}Don't miss the other page$\rightarrow$}
\phone{+46737-42 43 45}
\email{me@lukas.fyi}
%\photo[64pt][2pt]{./lukas.jpg}
\quote{"To an artificial mind, all reality is virtual."}
%\photo[64pt]{Yue_Yu}

\newcommand{\up}[1]{\ensuremath{^\textrm{\scriptsize#1}}}
\nopagenumbers{}

% the ConTeXt symbol
\def\ConTeXt{%
  C%
  \kern-.0333emo%
  \kern-.0333emn%
  \kern-.0667em\TeX%
  \kern-.0333emt}
\definecolor{web}{rgb}{0.2,0.2,0.2}
%------------------------------------\photo[64pt][0.4pt]{picture} ----------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{\textbf{Experience}}
\subsection{\textbf{IT Work}}
\cventry{2017 -- Current}{\textbf{Software Engineer}}{}{}{Klarna}
{Building the architecture for routing all payments and providing an uniform API to several underlaying services. Erlang and Scala.}
\cventry{2016 -- 2017}{\textbf{Developer}}{}{}{DICE (EA)}
{Built scalable backend services for Battlefield 1, 22M users 1.5M PSU}
\cventry{2014 -- 2015}{\textbf{Developer}}{}{}{Ericsson and SICS}
{Built an information centric network in Erlang for a live video streaming android application which we also built.
Deployed at the Skiing World Championship in Falun 2015.}
\cventry{2013}{\textbf{Lead Developer}}{}{}{London Sales (Australia)}
{Developed a large integration service for their systems. Also; an app, dashboard and CRM back-end. Mostly GWT, Java and .net.}
\cventry{2012}{\textbf{Developer}}{}{}{Kivra}
{Developing a massive online post system, mostly in Erlang.}
\cventry{2007 -- 2013}{\textbf{Websites}}{}{}{}
{Designing and developing a lot of websites for smaller companies and stores, for example the websites of the stores \begin{math}20m^2\end{math} skor and Cri Cri.}
\cventry{2008 -- 2011}{\textbf{Developer}}{}{}{RivCalc.com}
{A website written in GWT (Java syntax) to make mathematical calculations for a web-based game. Financed through google adsense.}
\cventry{2005 -- 2010}{\textbf{Tech/Computer support}}{}{}{}
{Both phone support and home visits.}
\newpage

\section{\textbf{Education}}
\cventry{2013--2015}{\textbf{Master of Computer Science}}{\newline University of Uppsala}{Sweden}{}{}
\cventry{2009--2012}{\textbf{Bachelor of Computer Science}}{\newline University of Uppsala}{Sweden}{}{}

\subsection{\textbf{Thesis}}
\cventry{}{\textbf{Master Thesis}}{Uprise}{Uppsala}{}{
A Security Management Layer for CDN Assets}
\cventry{}{\textbf{Bachelor Thesis}}{Kivra}{Stockholm}{}{
NoSQL: Moving from MapReduce Batch Jobs to Event-Driven Data Collection}

\subsection{\textbf{Some free time projects (More on GitHub)}}
\cventry{}{\textbf{MindLevel}}{}{}{}{
Written three times. Kotlin (Android) front-end and Scala backend, soon to be found in the play store}
\cventry{}{\textbf{Uratool}}{}{}{}{
A distributed collaborative coding editor written in Erlang.}
\cventry{}{\textbf{Esiade}}{}{}{}{
An Evolutionary simulator in a dynamic environment. Proof of concept of genetic programming and machine learning.}
\cventry{}{\textbf{Fork-Plate-Knife}}{}{}{}{
Small React (javascript) game made on the Uprise Game-Jam hackathon}

\renewcommand{\cvcomputer}[2]{\cvline{#1}{\small#2}}
\section{\textbf{Computer skills}}
\cvcomputer{OS}{Linux, Solaris, Windows, Mac OS X}
\cvcomputer{Programming}{Scala, Java, Erlang, Android, GWT, Javascript, C, Python, Haskell, Bash}
\cvcomputer{Databases}{MySql, MongoDB, Redis, Memcached, Riak, T-SQL}
\cvcomputer{Rev. control}{Git, Subversion, Mercurial}
\cvcomputer{Editors/IDE}{Vim, IntelliJ, Eclipse}
\cvcomputer{Typography}{\LaTeX, Office}
\cvcomputer{Other}{AWS Services,\newline
                   Containers,\newline
                   Pentesting,\newline 
                   System Administration,\newline 
                   Microcontroller Programming,\newline 
                   Data recovery,\newline 
                   Virus removal,\newline 
                   Hardware replacement}

\section{\textbf{Other}}
\subsection{\textbf{Details can be shown on request}}
\cventry{2006 -- Present}{\textbf{20+ Commisions of Trust}}{}{}{}{
Example: publicly elected board member of Uppsala Student Union}
\cventry{}{\textbf{Languages}}{}{}{}{English Fluently (Lived in Australia and England)\newline Swedish Mother Tounge\newline Spanish Basics (Backpacked Latin America)}
\cventry{}{\textbf{Random Fact}}{}{}{}{I have a Fork Bomb and a PRNG tattoed on my right arm}
%\cventry{}{\textbf{8 references}}{}{}{}{}

\end{document}
